\documentclass{article}

\begin{document}
\title{Individual Report}

\setlength{\parskip}{1em}

\author{John Burchell}
\maketitle

\subsection*{Responsibility and Requirements}

My main area of responsibility for the course was mostly concerned with the booking feature, this involved writing the use case description, use case, creating the sequence diagram, creating the activity diagram and finally the implementation and testing of the booking feature.
\par
All of the requirements which are assigned to me in the documentation have been implemented. However, this is not to say that all ideas we initially came up with were those that were implemented. There were numerous requirements that were suggested during the first few weeks that did not end up in the final implementation. One such example was a quote for a booking. It has been modelled to show where it would fit into the system but it was not implemented simply due to a lack of importance for that specific feature. Likewise, we initially discussed the idea of prioritising booking based on dates, times of the year e.t.c. but this was also not implemented in the final system for the same reasons.

\subsection*{Conflicts and Compromises}

As you are most likely aware, we have had a rather large conflict within the group mostly due to a lack of effort and work by certain members. Since the split of the group things have continued mostly in the same way but I feel it's worth mentioning that Sofie in particular really pulled her socks up and worked very hard in the remaining week before the Christmas break. 
\par
For day-to-day conflicts there were many, too many to note but they were more in the vein of being discussions and standard group work. As such I don't consider them to be in the same league as the previously mentioned conflict.

 Many of these discussions lead to compromises on requirements and features that were deemed necessary or not, we did not keep an exhaustive list of what these compromises were, as such the only ones that were thought of note have been included in the main documentation in our excluded section.

\subsection*{Actions}

This section is a condensation of my own diary which I (attempted) to keep up to date during the course. A note I would like to make is that, of the 5 core members (Myself, William, Patrik, Andam and Ioannis) we worked together on, if not all, almost all tasks as a group. The diary that I made consisted of tasks that I did either with other members of the group or by myself. We kept a group diary for tasks that we all participated in. This diary will be attached along side this as an appendix, please refer to it if you wish.
\par

The first week consisted of creating the initial requirements, mind map, domain model and getting our heads around how Papyrus works. During this week I partook in all activities notably in creating the initial requirements, mind map and domain research. I was also active during the refinement the requirements, domain model and the mind map.
\par

During the second week I partook in the refinement of dependencies in the domain model, refined the requirements based on feedback from our supervision session (and our own discussions) and a redistribution of the requirements. After the weekly supervision session we further refined the requirements and domain model. I worked mostly on the use-case diagram with William, partook in the creation of the vocabulary and worked with MaoMao on the use case descriptions.
\par
During week three I finalised the use case descriptions, partook in discussions about the domain model and refinement of requirements. I also helped to write the initial 3 business rules and started to create the real use cases. Later into this week we further refined the requirements, use case descriptions and the use case diagrams. This was done mainly to keep them in line with the vocabulary which had been finalised recently. Once again, after the supervision in that week, we spent a fair bit of time correcting and altering our documentation based on the feedback we were given.
\par
Week four saw the completion of the detail use cases, specifically for me that involved the make booking use case. We took the opportunity here to work on our other courses, as we felt that we were somewhat ahead or on schedule and as such not much more was completed this week.
\par
In week five William and I started to create the sequence diagram for Make Booking, we finalised this during the week and then created a version of it within Papyrus. After this was completed we then started to discuss the class diagram for the “Booking” component. On Thursday we had a rather large group discussion about the class diagrams and how the system would be created as a whole. By the end of the week we had finished the class diagram and had the classes arranged so that they correctly resembled the component diagram which had been created previously.
\par
Group 19' review was completed at the start of week six. Following this I worked closely with Andam based on Williams previous work to get the code generating correctly from our class diagram in the model. This continued for most of the week as we found many hiccups and peculiarities with the model that prevented the code from being generated in the way that we wanted. There were so many changes and tweaks done to the model during this phase that I didn't see a need to write them all down. 
\par
Week seven was much like week six in that we focused primarily upon implementation. Our aim was to be finished before the Christmas break as we would have a few members of the team being overseas and we simply wanted to have nothing hanging over our heads during Christmas and the new year. We spent the entire week working on the implementation, during this time I was mainly working on the booking module. I also liaised with Grischa to ask a few questions about implementation details, I looked into how we will be using the jar files in the end and many other various aspects of the system that are too numerous to mention. During the end of the week we all spent a considerable amount of time fixing the documentation and models to reflect changes that were made during the implementation phase of the project. 
\par

There were a few more alterations and additions to be made during week eight, I re-created the make booking sequence diagram based on the changes in its implementation and I also tidied up a few things in the code for the booking component. I made some changes to the makebooking method so that it was working correctly with the changes made to the make booking use case. I also packaged up the jar files and separated them from the test cases for the final hand in.



\end{document}
